### 2023-03-20 paper-thesis/chapters/10-coc.tex
Update presentation
Work a bit on thesis

The inference rules in figures \ref{fig:beta-head-reduce-rules}, \ref{fig:beta-eq-rules}, and \ref{fig:type-check-rules} can be directly translated to Statix rules. For example, the rule for \verb|Let| bindings in figure \ref{fig:type-check-rules} is expressed like this in Statix:
\begin{lstlisting}
typeOfExpr(s, Let(n, v, b)) = typeOfExpr(s', b) :-
    typeOfExpr(s, v) == vt, sPutSubst(s, n, (s, v)) == s'.
\end{lstlisting}

>>>>

The inference rules in figures \ref{fig:beta-head-reduce-rules}, \ref{fig:beta-eq-rules}, and \ref{fig:type-check-rules} can be directly translated to Statix rules. For example, the rule for \verb|Let| bindings in figure \ref{fig:type-check-rules} is expressed like this in Statix:
\begin{lstlisting}
typeOfExpr (s, Let(x, e, b)) = bt :-
	typeOfExpr (s, e) == et, 
	typeOfExpr (sPutSubst (s, x, (s, e)), b) == bt.
\end{lstlisting}

Each premise in the inference rule is a premise in the Statix code, and the conclusion of the inference rule is the declaration of the Statix rule.

### 2023-03-20 paper-thesis/chapters/11-variable-capture.tex
Work a bit on thesis

An example term where this problem occurs is the following: What is the type of this expression (a polymorphic identity function)?
\begin{lstlisting}
\T : Type. \T : T. T
\end{lstlisting}
The implementation so far would tell you it is \verb|T : Type -> T : T -> T| \todo{why is this wrong}. Given the scoping rules of the language, that is equivalent to \verb|T : Type -> x : T -> x|. However, the correct answer would be \verb|T : Type -> x : T -> T|. There is no way of expressing this type without renaming a variable.

>>>>

An example term where this problem occurs is the following: What is the type of this expression (a polymorphic identity function)?
\begin{lstlisting}
\T : Type. \T : T. T
\end{lstlisting}
The implementation so far would tell you it is \verb|T : Type -> T : T -> T|. Given the scoping rules of the language, that is equivalent to \verb|T : Type -> x : T -> x|. Note that \verb|x| is not a type, so this does not even type check. The correct answer would be \verb|T : Type -> x : T -> T|. There is no way of expressing this type without renaming a variable.

### 2023-03-20 paper-thesis/chapters/21-adding-inference.tex
Add todo
Work on CoC chapter
Add chapter transitions
Work a bit on thesis

Inference is an important feature of dependent programming languages, that allows redundant parts of programs to be left out. For example, it allows you to infer the arguments of a function, if they can be inferred by the arguments that follow, like here where the type of the argument can be inferred, since we pass it \verb|true| which is a boolean:
\begin{lstlisting}
let id = (\T : Type. \x: T. x);
id _ true
\end{lstlisting}

We call it \emph{term inference} rather than \emph{type inference}, because we can infer values other than types. For example, it can infer that the \verb|_| in this example must be \verb|true|:
\begin{lstlisting}
postulate f: Bool -> Type;
postulate g: f true -> Type;
\x: f _. g x
\end{lstlisting}

\section{Different algorithms for inference}
\label{strength-inference}

@@

\section{Analysis of the approximation}
\label{analysing-inference}

@@

>>>>

Inference is an important feature of dependent programming languages, that allows redundant parts of programs to be left out. For example, it allows you to infer the argument type of a function, if it can be inferred by the usage of the function, like in this example where the type of the argument of the polymorphic identity function can be inferred, since we pass it \verb|true| which is a boolean:
\begin{lstlisting}
let id = (\T : Type. \x: T. x);
id _ true
\end{lstlisting}

The syntax we chose is that if we want a value to be inferred, we replace it with an underscore. Other languages such as Agda allow for \emph{implicit arguments}, which are arguments that can be left out, which will then be inferred~\cite{agda}~\cite{coq}. This is just syntactic sugar over the \emph{placeholders} we implement.

Furthermore, we call the inference algorithm \emph{term inference} rather than \emph{type inference}, because it can infer values other than types. For example, it can infer that the placeholder in this example must be \verb|true|:
\begin{lstlisting}
postulate f: Bool -> Type;
postulate g: f true -> Type;
\x: f _. g x
\end{lstlisting}

\section{Different Algorithms for Inference}
\label{strength-inference}

@@

\section{Analysis of the Approximation}
\label{analysing-inference}

@@

\todo{Mention Equational Unification as a solution}

We have now shown how to add inference to the implementation. Next, we will add Inductive Datatypes (chapter~\ref{ch:datatypes}) and Universes (chapter~\ref{ch:universes}) to the implementation.
